P2.Data.Exploration

### 2021-11-12 code/processing_code/ProcessingScript.Rmd
Clean up and Temp Code
Clean up of unused scripts and removal of knitted items. Temp Code added-- working on doing a completely automated data import from reports.

---
title: "Data Processing and Saving"
author: "MYC"
date: "10/29/2021"
output: 
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type:
---
Loading all the default settings and preliminary programs.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #for data processing and all dplyr related programs
library(here)      #to set paths
library(lubridate) # for date manipulation
library(broom)    #for tidying up if needed

>>>>

---
title: "Data Processing and Saving"
author: "MYC"
date: "10/29/2021"
output: 
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type:
---
This script loads the 2021-10-23_All.Update.csv, a composite of reports, from `raw-data`.
The script further processes, cleans, splits, and saves the data as rds files in the `processed_data` folder.

Loading all the default settings and preliminary programs.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #for data processing and all dplyr related programs
library(here)      #to set paths
library(lubridate) # for date manipulation
library(broom)    #for tidying up if needed

### 2021-11-12 code/processing_code/TEMP/P2.Data.Exploration.rmd
Clean up and Temp Code
Clean up of unused scripts and removal of knitted items. Temp Code added-- working on doing a completely automated data import from reports.

---
title: "P2.Data.Exploration"
author: "MYC"
date: "10/25/2021"
output: 
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type: console
---
Loading all the default settings and preliminary programs.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #for data processing and all dplyr related programs
library(here)      #to set paths
library(tidymodels)      # for the recipes package, along with the rest of tidymodels
library(skimr)           # for variable summaries

>>>>

---
title: "P2.Data.Exploration"
author: "MYC"
date: "10/25/2021"
output: 
  html_document:
    theme: cosmo
---
Loading all the default settings and preliminary programs.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #for data processing and all dplyr related programs
library(here)      #to set paths
library(tidymodels)      # for the recipes package, along with the rest of tidymodels
library(skimr)           # for variable summaries
